Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Updated Paper

---
title: "Forecasting the 2024 U.S. Presidential Election"
author: 
  - Jason Yang
  - Another author
thanks: "Code and data are available at: [https://github.com/Jerryx2020/US_election_prediction/tree/main]."
date: "`r format(Sys.Date() - 1, '%A, %B %d, %Y')`" #chatgpt assisted how to create a custom date for due date November 4
date-format: long
abstract: "This paper presents a multiple linear regression model and a bayesian model for forecasting the outcome of the 2024 U.S. Presidential Election. Using the data collected from high-quality polls from various pollsters, we generate these models by selecting relevant variables such as sample size, percentage support for each candidate, and sate. By comparing the predictive power of both models, we aim to provide a reliable forecast of the election outcome and a deeper understanding of public sentiment and polling reliability."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

@@

\begin{align*}
\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{sample\_size}_i + \beta_3 \cdot \text{transparency\_score}_i \\
&\quad + \sum_{k=1}^{K} \delta_k \cdot \text{state}_{ik} + \beta_4 \cdot \text{end\_date}_i + \epsilon_i,
\end{align*}

- pct: The percentage of the vote or support that the candidate received in the poll (e.g., 51.0 for Kamala Harris, 48.0 for Donald Trump).
- numeric_grade: A numeric rating given to the pollster to indicate their quality or reliability (e.g., 3.0).
- sample_size: The total number of respondents participating in the poll (e.g., 2712).
- transparency_score:A score reflecting the pollster’s transparency about their methodology (e.g., 9.0). "A grade for how transparent a pollster is, calculated based on how much information it discloses about its polls and weighted by recency. The highest Transparency Score is 10."
- state: The U.S. state where the poll was conducted or focused, if applicable.
- end_date: The date the poll ended (e.g., 10/11/24).
- $\epsilon_i$: The error term for poll accounting for variability not explained by the predictors.

@@

```{r}
#| tbl-cap: Checking Assumptions
#| echo: false
#| eval: true
#| warning: false
#| message: false

linear_model <- readRDS(here::here("models/linear_model.rds"))

plot(linear_model$fitted.values, residuals(linear_model), 
     main = "Residuals vs Fitted", 
     xlab = "Fitted values", 
     ylab = "Residuals")

# Q-Q Plot for Normality
qqnorm(residuals(linear_model))
qqline(residuals(linear_model))

```
In the Residuals vs. Fitted, there is no clear curved pattern, which suggests that the linear relationship might be appropriate. However, there are some clusters and a slight spread, which may indicate minor issues in capturing the relationship fully. Secondly, in the qqnorm plot, the points closely follow the diagonal line, indicating that residuals are approximately normal. This supports the normality assumption of the residuals, which is essential for reliable inference in linear regression.

@@

The proposed survey is designed using Google Forms,
https://docs.google.com/forms/d/e/1FAIpQLSeHHeKaryNQ6sKgbuOH-ZgXwQYkNw9jBdxIbgeXWVj_t1ob2w/viewform?usp=sf_link

## Survey Copy

@@

>>>>

---
title: "Forecasting the 2024 U.S. Presidential Election"
author: 
  - Jason Yang
  - Another author
thanks: "Code and data are available at: [https://github.com/Jerryx2020/US_election_prediction/tree/main]."
date: "`r format(Sys.Date() - 1, '%A, %B %d, %Y')`" #chatgpt assisted how to create a custom date for due date November 4
date-format: long
abstract: ""
format: pdf
number-sections: true
bibliography: references.bib
---

@@

To accurately predict the 2024 Presidential Election, we have identified several key variables that capture a range of factors influencing voter behavior. These predictor variables include:

- Polling Percentage (PCT): Represents the percentage of respondents in a poll who support a specific candidate
- Numeric Grade (numeric_grade): Represents the rating of the pollster to indicate their quality
- Sample Size (sample_size): size of the respondents participating in the poll
- State (state): the state of the poll was taken in 
- End_date: the day the poll ended
- Start_date: the day the poll started

@@

\begin{align*}
\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{sample\_size}_i + \sum_{k=1}^{K} \delta_k \cdot \text{state}_{ik} + \beta_4 \cdot \text{end\_date}_i + \epsilon_i,
\end{align*}

- pct: The percentage of the vote or support that the candidate received in the poll (e.g., 51.0 for Kamala Harris, 48.0 for Donald Trump).
- numeric_grade: A numeric rating given to the pollster to indicate their quality or reliability (e.g., 3.0).
- sample_size: The total number of respondents participating in the poll (e.g., 2712).
- state: The U.S. state where the poll was conducted or focused, if applicable.
- end_date: The date the poll ended (e.g., 10/11/24).
- $\epsilon_i$: The error term for poll accounting for variability not explained by the predictors.

@@

In the Residuals vs. Fitted, there is no clear curved pattern, which suggests that the linear relationship might be appropriate. However, there are some clusters and a slight spread, which may indicate minor issues in capturing the relationship fully. Secondly, in the qqnorm plot, the points closely follow the diagonal line, indicating that residuals are approximately normal. This supports the normality assumption of the residuals, which is essential for reliable inference in linear regression.

@@

The proposed survey is designed using Google Forms,
https://forms.gle/Vhmm1b1XnqTSoBWq8

## Survey Copy 
Welcome to our survey! We are conducting research to understand public perceptions and opinions related to the upcoming 2024 Presidential Election. Your responses are valuable in helping us gain insight into voter perspectives and preferences.

Contact Information: For any questions regarding this survey, please contact:

Name: [Jason Yang]
Email: ["jzc.yang@mail.utoronto.ca"]
Phone: ["123-234-5678"]

Your responses are confidential and will be used only for research purposes. This survey will take approximately [estimated time] to complete.

@@

Thank you for taking the time to complete our survey. Your input is greatly appreciated and will contribute to our understanding of public opinion for the upcoming 2024 Presidential Election.
